Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-02 overleaf/paper_SIMD.tex
Reorganized sections again...
Changed Lindsey's email.
added LAN benchmarks to the paper
add updated graphs
wip evaluation section
Edits to Results.
Changes to results and related work.
red line numbers return
Removed Conf. info.

% !TeX TXS-program:compile = txs:///pdflatex/[--shell-escape]
%
% acm templates v1.57 (sigconf template)
%
%\documentclass[sigconf, screen, review, anonymous, natbib=false]{acmart}
\documentclass[sigconf, screen, natbib=false, dvipsnames, table]{acmart}
\settopmatter{printacmref=true}
% mandatory for CCS'19
\usepackage{balance}
\usepackage{mathtools}
% for creating a balanced last page (usually last page with references)

@@

\copyrightyear{2019}
\acmYear{2019}
\setcopyright{acmcopyright}
\acmConference[CCS '19]{2019 ACM SIGSAC Conference on Computer and Communications Security}{November 11--15, 2019}{London, United Kingdom}
\acmBooktitle{2019 ACM SIGSAC Conference on Computer and Communications Security (CCS '19), November 11--15, 2019, London, United Kingdom}
\acmPrice{15.00}
\acmDOI{10.1145/3319535.3339818}
\acmISBN{978-1-4503-6747-9/19/11}

@@

% *** GRAPHICS RELATED PACKAGES ***
\usepackage{graphicx}
\usepackage{comment}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{listings}
% declare the path(s) where your graphic files are
\graphicspath{{../figures/}}
% and their extensions so you won't have to specify these with
% every instance of \includegraphics
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}

@@

\sloppy
\begin{document}
\fancyhead{}
% do not delete this code.

@@

\author{Lindsey Kennard}
\email{fire.elemental@gmail.com}
\affiliation{%
    \institution{STR}
    %\streetaddress{1 Th{\o}rv{\"a}ld Circle}
    \city{Boston}
    \state{Massachusets}
    %\country{Iceland}
}

@@

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003752.10010124.10010138.10010143</concept_id>
<concept_desc>Theory of computation~Program analysis</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10003777.10003789</concept_id>
<concept_desc>Theory of computation~Cryptographic protocols</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002978.10002979</concept_id>
<concept_desc>Security and privacy~Cryptography</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

@@

%
% Keywords. The author(s) should pick words that accurately describe the work being
% presented. Separate the keywords with commas.
\keywords{multiparty computation; compilers; cryptography}

\begin{comment}
%
% A "teaser" image appears between the author and affiliation information and the body
% of the document, and typically spans the page.
\begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{Seattle Mariners at Spring Training, 2010.}
    \Description{Enjoying the baseball game from the third-base seats. Ichiro Suzuki preparing to bat.}
    \label{fig:teaser}
\end{teaserfigure}
\end{comment}
%
% This command processes the author and affiliation and title information and builds
% the first part of the formatted document.
\maketitle

@@

% Compiler Framework Section
\input{compiler.tex}

@@

@@

\section{Conclusion and Future Work}
\label{sec:conclusion}
%\input{../sections/conclusion.tex}

>>>>

% !TeX TXS-program:compile = txs:///pdflatex/[--shell-escape]
%
% acm templates v1.57 (sigconf template)
%
\documentclass[sigconf, screen, review, anonymous, natbib=false, dvipsnames, table]{acmart}
%\documentclass[sigconf, screen, natbib=false, dvipsnames, table]{acmart}
\settopmatter{printacmref=false}
\renewcommand\footnotetextcopyrightpermission[1]{}
% mandatory for CCS'19
\usepackage{balance}
\usepackage{mathtools}
% for creating a balanced last page (usually last page with references)

@@

%\copyrightyear{2019}
%\acmYear{2019}
%\setcopyright{acmcopyright}
%\acmConference[CCS '19]{2019 ACM SIGSAC Conference on Computer and Communications Security}{November 11--15, 2019}{London, United Kingdom}
%\acmBooktitle{2019 ACM SIGSAC Conference on Computer and Communications Security (CCS '19), November 11--15, 2019, London, United Kingdom}
%\acmPrice{15.00}
%\acmDOI{10.1145/3319535.3339818}
%\acmISBN{978-1-4503-6747-9/19/11}

@@

% *** GRAPHICS RELATED PACKAGES ***
\usepackage{graphicx}
\usepackage{comment}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{listings}
% declare the path(s) where your graphic files are
\graphicspath{{../figures/}{graphs/}{graphs/lan/}}
% and their extensions so you won't have to specify these with
% every instance of \includegraphics
\DeclareGraphicsExtensions{.pdf,.jpeg,.png, .eps}

@@

\sloppy
\begin{document}
% \fancyhead{}
% do not delete this code.

@@

\author{Lindsey Kennard}
\email{fireelemental.ne@gmail.com}
\affiliation{%
    \institution{STR}
    %\streetaddress{1 Th{\o}rv{\"a}ld Circle}
    \city{Boston}
    \state{Massachusets}
    %\country{Iceland}
}

@@

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%
\begin{comment}
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003752.10010124.10010138.10010143</concept_id>
<concept_desc>Theory of computation~Program analysis</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10003777.10003789</concept_id>
<concept_desc>Theory of computation~Cryptographic protocols</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002978.10002979</concept_id>
<concept_desc>Security and privacy~Cryptography</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

@@

%
% Keywords. The author(s) should pick words that accurately describe the work being
% presented. Separate the keywords with commas.
\keywords{multiparty computation; compilers; cryptography}
\end{comment}

\begin{comment}
%
% A "teaser" image appears between the author and affiliation information and the body
% of the document, and typically spans the page.
\begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{Seattle Mariners at Spring Training, 2010.}
    \Description{Enjoying the baseball game from the third-base seats. Ichiro Suzuki preparing to bat.}
    \label{fig:teaser}
\end{teaserfigure}
\end{comment}
%
% This command processes the author and affiliation and title information and builds
% the first part of the formatted document.
\maketitle
\thispagestyle{empty}

@@

% Compiler Front End
\input{compiler.tex}

@@

% Backend
\input{backend.tex}

@@

\section{Conclusion and Future Work}
\label{sec:conclusion}

\ana{Need a conclusion here!}

%\input{../sections/conclusion.tex}
